The Talking Heads Experiment

### 2015-04-16 chap1/chap1.tex
corrected minor mistake from previous commit
minor changes

The Talking Heads experiment follows this research strategy. \is{Talking Heads Experiment}
It features an enormously challenging experimental
infrastructure to explore how a cognitive
system, like the one underlying human language, might
be able to bootstrap itself into interaction 
with other cognitive systems and driven by increasing
challenges from the environment. The experiment
involves a set of robotic `Talking Heads' engaged in language
games, with each other or with human interlocutors, 
about real world scenes they perceive through their sensors
(see Figures \ref{f:plate1} and \ref{f:plate2}).
The robots use vision as major sensory source. They are located in
different places in the world and connected through the Internet. 
Two robotic agents can only engage in an interaction when they 
are instantiated in robot bodies in a shared physical environment. 
After an exchange, an agent can teleport himself to another body in 
another location and engage in interactions there.

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.40\textwidth]{./chap1/figs/head.pdf}}
\caption{A single `Talking Head'. There is a camera oriented towards a
white board. The bottom screen shows what the camera observes. The top right screen shows the result of processing.
A loudspeaker reproduces the utterances of the agent. }
\label{f:plate2}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap1/figs/fish.pdf}}
\caption{`Artificial fish' built by Miles Pebody to explore influence of robot bodies on behaviour. The fish could swim around by wagging 
its tail and avoid obstacles based on infrared sensing.}
\label{f:plate4}
\end{figure}

>>>>

The Talking Heads experiment follows this research strategy. \is{Talking Heads Experiment}
It features an enormously challenging experimental
infrastructure to explore how a cognitive
system, like the one underlying human language, might
be able to bootstrap itself into interaction 
with other cognitive systems and driven by increasing
challenges from the environment. The experiment
involves a set of robotic ``Talking Heads'' engaged in language
games, with each other or with human interlocutors, 
about real world scenes they perceive through their sensors
(see Figures \ref{f:plate1} and \ref{f:plate2}).
The robots use vision as major sensory source. They are located in
different places in the world and connected through the Internet. 
Two robotic agents can only engage in an interaction when they 
are instantiated in robot bodies in a shared physical environment. 
After an exchange, an agent can teleport himself to another body in 
another location and engage in interactions there.

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.40\textwidth]{./chap1/figs/head.pdf}}
\caption{A single ``Talking Head''. There is a camera oriented towards a
white board. The bottom screen shows what the camera observes. The top right screen shows the result of processing.
A loudspeaker reproduces the utterances of the agent. }
\label{f:plate2}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap1/figs/fish.pdf}}
\caption{``Artificial fish'' built by Miles Pebody to explore influence of robot bodies on behaviour. The fish could swim around by wagging 
its tail and avoid obstacles based on infrared sensing.}
\label{f:plate4}
\end{figure}

### 2015-04-16 chap2/chap2.tex
cumulative update, mainly for Ch. 7-12
minor changes

\begin{table}[htbp]
\caption{}
\label{tab:2:findthereferent}
\begin{tabular}{ l  l  l  l }
\lsptoprule
{\itshape Activity} & {\itshape From} & {\itshape To} & {\itshape Knowledge source}\\ \midrule
Perceive & Object & Image segments & Visual processes \\ 
Conceptualise & Topic & Meaning & Ontology  \\ 
Verbalise & Meaning & Utterance & Lexicon + syntax \\  
Interpret & Utterance & Meaning & Lexicon + syntax \\ 
Apply & Meaning & Topic & Ontology \\ 
Act & Topic & Object & Behavioural process  \\ 
\lspbottomrule
\end{tabular}
\end{table}

There is no simple linear flow from perception to utterance 
or from utterance to perception. Instead, we must imagine a dynamic process 
involving forward and backward propagation of information 
until coherent choices for all the nodes in the two
semiotic squares have been established by the speaker and 
the hearer. Many different choices are initially possible 
(many segmentations, conceptualisations, verbalisations, 
interpretations), but the dynamic process gradually settles into 
a single coherent attractor, so that speaker and hearer 
agree upon a common referent. The co-ordination between 
chosen topic and identified referent is done through 
the real world (pointing, handing an object, performing
an action).

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=\textwidth]{chap2/figs/competition-1.pdf}}
\caption{\label{competition1} 
The graph shows the competition between different forms for
expressing one meaning in a population of 20 agents. The graph plots 
the frequency of each form in the population, more precisely the percentage
of agents that prefer a particular word. A complex dynamic
process unfolds with periods where one word (first `xu' and then `fepi') dominates.} 
\end{figure}

>>>>

\begin{table}[htbp]
\caption{}
\label{tab:2:findthereferent}
\begin{tabular}{ l  l  l  l }
\lsptoprule
{\itshape Activity} & {\itshape From} & {\itshape To} & {\itshape Knowledge source}\\ \midrule
Perceive & Object & Image segments & Visual processes \\ 
Conceptualise & Topic & Meaning & Ontology  \\ 
Verbalise & Meaning & Utterance & Lexicon + syntax \\  
Interpret & Utterance & Meaning & Lexicon + syntax \\ 
Apply & Meaning & Topic & Ontology \\ 
Act & Topic & Object & Behavioural process  \\ 
\lspbottomrule
\end{tabular}
\end{table}
\todo[inline]{This table needs a caption}
There is no simple linear flow from perception to utterance 
or from utterance to perception. Instead, we must imagine a dynamic process 
involving forward and backward propagation of information 
until coherent choices for all the nodes in the two
semiotic squares have been established by the speaker and 
the hearer. Many different choices are initially possible 
(many segmentations, conceptualisations, verbalisations, 
interpretations), but the dynamic process gradually settles into 
a single coherent attractor, so that speaker and hearer 
agree upon a common referent. The co-ordination between 
chosen topic and identified referent is done through 
the real world (pointing, handing an object, performing
an action).

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=\textwidth]{chap2/figs/competition-1.pdf}}
\caption{\label{competition1}The graph shows the competition between different forms for
expressing one meaning in a population of 20 agents. The graph plots 
the frequency of each form in the population, more precisely the percentage
of agents that prefer a particular word. A complex dynamic
process unfolds with periods where one word (first `xu' and then `fepi') dominates.} 
\end{figure}
